% LaTeX resume using res.cls
\documentclass[line,margin]{res}
\usepackage{hyperref}
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{colorlinks=true, urlcolor=cyan}


\begin{document}
\name{Simon Crowe | Cloud-Native Software Engineer}
% \address can be used twice for additional contact info
\address{}
\address{\href{mailto://simon.r.crowe@protonmail.com}{simon.r.crowe@protonmail.com}}


\begin{resume}

\section{SUMMARY} Experienced in building and maintaining event-driven backends and platform tooling
                  on Kubernetes and AWS. While I'm comfortable writing product-facing APIs,
                  I work best at the intersection of application code and infrastructure:
                  designing processing pipelines, improving developer experience, and solving problems that
                  span service boundaries. I have a track record of raising engineering standards
                  through style guides, API conventions, and architectural patterns.
                  I feel at home with a DevOps culture and being on-call.

\section{SKILLS} {\sl \textbf{Languages:}} Python, SQL, Bash\\
                 {\sl \textbf{Cloud \& Infrastructure:}} AWS, Kubernetes, Terraform, Docker, Helm\\
                 {\sl \textbf{Data \& Messaging:}} Kafka, PostgreSQL, Redis\\
                 {\sl \textbf{Frameworks \& Libraries:}} FastAPI, Django, pytest\\
                 {\sl \textbf{Observability:}} OpenTelemetry, structlog, OpenSearch, Cloudwatch, Honeycomb\\
                 {\sl \textbf{Some exposure to:}} Javascript, Go, Rust, GCP

\section{EXPERIENCE} \textbf{Medtronic Digital Surgery} \\
                {\sl Senior Software Engineer} \hfill   Feb 2022 - present \\
                 \begin{itemize}  \itemsep  -0pt
                   \item Designed and implemented a video processing orchestrator using Kubernetes, FastAPI and Kafka
                         that replaced AWS MediaConvert in 97\% of cases, saving an estimated \$280,000 annually.
                         Instrumented the service with OpenTelemetry distributed tracing and structured logging throughout.
                   \item Migrated Kafka topic management to Strimzi topic operator, replacing single-partition topics
                         with properly scaled configurations to support parallel consumers.
                         Switched cluster authentication from MTLS (which had become costly and ineffective) to IAM.
                   \item Developed a fault-tolerant serverless solution for sending S3 objects to HTTP APIs as a
                         reusable Terraform module, adopted by multiple teams for event delivery to the data platform.
                   \item Enabled multi-AZ scheduling for GPU workloads running ML inference and ffmpeg,
                         improving availability over the previous single-AZ setup.
                   \item Pioneered structured logging across the main Django monolith;
                         modified workloads to emit logs to STDOUT for centralised collection.
                   \item Re-architected a legacy Git/LFS assets server for multi-region cloud deployments.
                   \item Replaced long-lived AWS IAM user credentials used in CI/CD with least-privilege assumed roles.
                   \item Re-wrote legacy video processing integration tests in pytest, replacing an ad-hoc Python script.
                         Reduced worst-case failure feedback time from 90 to 30 minutes.
                   \item Authored a Python style guide and an engineering-wide document on HTTP API conventions,
                         both adopted as team standards.
                 \end{itemize}
                {\sl Platform Engineer} \hfill          Nov 2019 - Feb 2022 \\
                  \begin{itemize}  \itemsep -0pt
                  \item Led the implementation of MFA in line with OAuth 2.0 Best Current Practice.
                  \item Unified multiple video-sharing features, resolving data integrity issues
                        and simplifying the path for future sharing functionality.
                  \item Implemented backend for allowing users to download surgical videos.
                  \item Championed the service layer pattern to extract business logic from Django models,
                        improving testability and separation of concerns.
                  \end{itemize}

                \textbf{Verv} \\
                {\sl Python Developer} \hfill        Jun 2019 - Nov 2019 \\
                  \begin{itemize} \itemsep -0pt
                  \item Contributed to Python codebase of IoT energy monitoring device;
                        developed PoC for a Bluetooth GATT server.
                  \end{itemize}

                \textbf{Ubiquity Press} \\
                {\sl Software Developer} \hfill        May 2018 - Jun 2019 \\
                  \begin{itemize} \itemsep -0pt
                  \item Migrated legacy Django applications from manual SSH deployments
                        to continuous delivery pipelines using Docker, Kubernetes and Helm.
                  \item Built the foundations of an internal platform for deploying and managing
                        web applications, with RBAC and $>$80\% test coverage.
                  \end{itemize}

	        \textbf{Titan Labs} \\
                {\sl Software Engineer} \hfill         Sep 2017 - Apr 2018 \\
                  \begin{itemize} \itemsep -0pt
                  \item Independently implemented a PoC recommender system using LightFM
                        to speed up client consultations.
                  \item Designed, built and documented REST APIs using Flask and OpenAPI 2.0.
                  \end{itemize}

\section{CERTIFICATIONS} CKAD: Certified Kubernetes Application Developer \hfill Feb 2025 \\
                         AWS Certified Solutions Architect -- Associate \hfill Mar 2024

\section{INTERESTS} Personal projects: \url{https://github.com/simoncrowe} \\
                    Active Blog: \url{https://simoncrowe.blog} \\
                    Cloud-focussed Engineering Blog: \url{https://simoncrowe.hashnode.dev} \\
                    Hobbies: running, strength training, reading, music, art

\section{EDUCATION} {\sl MA, Digital Culture} | Goldsmiths, University of London \hfill 2016 - 2017 \\
                    {\sl BA, Fine Art} | Loughborough University\hfill 2009 - 2013

\end{resume}
\end{document}
